### 2012-01-10 docs/SDC/sdc.tex
add intro

@@

>>>>

\subsection{Introduction to SDC}

@@

By default, \maestro\ uses an operator-split approach to coupling
the different physical processes together (hydro, reactions, diffusion).
With operator-splitting, we
react for a half timestep, then perform the hydrodynamics and thermal
diffusion on this intermediate state, and finally react for the
remaining half timestep to advance the solution.  For problems where
the reactions greatly alter the energy balance or composition, this
operator splitting approach can lead to inaccuracies in the solution.
This can be more of an issue for low Mach number methods that can take
large hydrodynamic time steps.

An alternate approach to coupling is spectral deferred corrections
(SDC). SDC is an iterative approach to couple the various operations
together, with each operator seeing an iteratively lagged
approximation of the other operations as a source term.  The SDC
algorithm converges to an integral representation of the solution in
time that couples all of the processes together in a self-consistent
fashion, see \cite{Non11}.

As a first attempt, we will work on coupling hydro and reactions only
via SDC, with a time-independent base state.
